### 2017-03-15 ResearchNotes/stat_exps.tex
Adds information on experiments to research notes

\chapter{Statistics and Experiments}

@@

@@

>>>>

\chapter{Statistics, Datasets, and Experiments}

@@

\subsection{\texttt{STAT\_007} - Number of Students per Course and Number of
Approved Students per Course}

We plot what the title states. The grey bars show the number of students
overall. The blue bars show the number of approved students. Each bar is one
course. Figure~\ref{fig_stat_007} shows the results of this statistics.

    \includegraphics[width=\linewidth]{../src/stat_007_results/plot}

    \caption
        [Number of Students per Course and Number of Approved Students per
        Course]
        {Number of Students per Course and Number of Approved Students per
        Course.}

    \label{fig:stat_007}
\end{figure}

% =============================================================================
\section{Datasets}

\subsection{\texttt{DAT\_001} - Students, Courses, Logs, and Results}
\label{sec:dat_001}

This dataset, which features is presented in table~\ref{tar:dat_001}, takes
information from the following datasets:

\begin{itemize}
    \item \texttt{Students}
    \item \texttt{CoursesGeneral}
    \item \texttt{MoodleLogs}
    \item \texttt{Results}
\end{itemize}

Each object of the dataset contains information referencing a single student in
a single course. The objects contain the overall enrollment count and type of
student. It also contain the identification of a course along with the semester
and season of that course. Finally, the object contains a count of CRUD
activities of that student in that course.

The dataset can be generated with different classes. There are three options.
Option one, the classes is a binary features which has the value true if the
student was approved on that course, and false otherwise. Option two, the class
has one of the following values which are intervals of grades:

\begin{itemize}
    \item $ [0, 10[ $
    \item $ [10, 12[ $
    \item $ [12, 14[ $
    \item $ [14, 16[ $
    \item $ [16, 18[ $
    \item $ [18, 20] $
\end{itemize}

Option three, the class has one of the following values:

\begin{itemize}
    \item $ [0, 10[ $
    \item $ [10, 14[ $
    \item $ [14, 18[ $
    \item $ [18, 20] $
\end{itemize}

With option two, we get a dataset which groups every records with grades below
10, but separates the positive grades in groups of two. Option three does the
same but separates grades into groups of four, with the last group having only
three values instead of 4.

    \begin{tabular}{| l | l | l |}
        \hline
        \textbf{Field}             & \textbf{Source Dataset}    & \textbf{Type} \\ \hline
        \texttt{EnrollementCount}  & Student                    & Number        \\ \hline
        \texttt{StudentType}       & Student                    & Enumerated    \\ \hline
        \texttt{CourseCodeSiiue}   & CoursesGeneral             & String        \\ \hline
        \texttt{Semester}          & CoursesGeneral             & Enumerated    \\ \hline
        \texttt{Season}            & CoursesGeneral             & Enumerated    \\ \hline
        \texttt{TotalActsOnCourse} & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{CActsOnCourse}     & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{RActsOnCourse}     & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{UActsOnCourse}     & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{DActsOnCourse}     & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{Class}             & Calculated From Results    & Binary        \\ \hline
    \end{tabular}

    \caption
        [Dataset 001]
        {Dataset 001}

    \label{tab:dat_001}
\end{table}

\subsection{\texttt{DAT\_002} - Results and Logs}
\label{sec:dat_002}

This dataset only contains features which a number type. Each object is
calculated from the records of a single student and relates the number of
enrolled courses, number of approved courses, number of each CRUD activity and
overall number of activities. The records come from the \texttt{Results} and
\texttt{MoodleLogs} datasets. Table~\ref{tab_dat_002} shows the features of
this dataset.

    \begin{tabular}{| l | l | l |}
        \hline
        \textbf{Field}           & \textbf{Source Dataset}    & \textbf{Type} \\ \hline
        \texttt{EnrolledCourses} & Calculated From Results    & Number        \\ \hline
        \texttt{ApprovedCourses} & Calculated From Results    & Number        \\ \hline
        \texttt{ActSumAll}       & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{ActSumC}         & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{ActSumR}         & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{ActSumU}         & Calculated From MoodleLogs & Number        \\ \hline
        \texttt{ActSumD}         & Calculated From MoodleLogs & Number        \\ \hline
    \end{tabular}

    \caption
        [Dataset 002]
        {Dataset 002}

    \label{tab:dat_002}
\end{table}

@@

This section gives a very brief overview of the experiments run for this
project. The actual explanation and interpretation of them is written in the
thesis text.

\subsection{\texttt{EXP\_001} - Predicting Students Grades Based on Moodle
Usage}

Experiment uses \texttt{DAT\_001}, described in section~\ref{sec:dat_001}.

\begin{verbatim}
Tree Binary and Bayesian Binary
Conclusion: More activity -> approved

Tree 4 and Bayesian 4
Conclusion: More activity -> approved
Conclusion: More number of CRUD -> better grade
Conclusion: More updates -> better grades

Tree 2 and Bayesian 2
Conclusion: More activity -> approved
Conclusion: More number of CRUD -> better grade
Conclusion: More updates -> better grades
\end{verbatim}

\subsection{\texttt{EXP\_002} - Clustering Moodle Usage Data}

Experiment uses \texttt{DAT\_001}, described in section~\ref{sec:dat_001}.

\begin{verbatim}
Two clusters
Conclusion: Clusters are found in users with different number of CRUD
activities. Silhouette score isn't that great
\end{verbatim}

\subsection{\texttt{EXP\_003} - Predicting Number of Approved Courses Based on
Moodle Usage}

Experiment uses \texttt{DAT\_002}, described in section~\ref{sec:dat_002}.

\begin{verbatim}
Tree and Bayesian with original, 2, 4, or 6
Conclusion: Based on the activity and number of enrolled courses we can
predict the number of approved courses with great accuracy!
\end{verbatim}

\subsection{\texttt{EXP\_004} - clustering Number of Approved Courses Based on
Moodle Usage}

Experiment uses \texttt{DAT\_002}, described in section~\ref{sec:dat_002}.

\begin{verbatim}
Results are similar to EXP_002
\end{verbatim}
